References for PloS paper

### 2014-01-13 image_analysis_paper/plos_draft.tex
Added more to report

The issue of rotation invariance arises in many applications, such as medical imaging \cite{hajnal2010medical}, face recognition \cite{rowley1998rotation}, digit recognition \cite{simard1992efficient}, and texture classification \cite{greenspan1994rotation}.
%
In these settings, objects from different frames or timepoints must be aligned or ``registered'' before further analysis can be done.
%
%For example, often medical images (such as MRI scans) are collected over multiple days, and doctors would like to study development of a condition (such as the growth of a tumor).
%
%However, on each day, the patient and/or sensors may be in slightly different locations; therefore, the images must be aligned before the doctor can look at how the tumor is growing and evolving.
%
Several different techniques have been developed to solve the image registration problem. 
%
``Template-based'' techniques, where one selects a prototypical image or ``template'', and then aligns the remaining images to this template \cite{ahuja2007template}.
%
Such techniques can suffer if a good template is not know {\em a priori}; when the images are noisy, selecting one image from the data set at random can yield a noisy template and result in many mis-alignments. 
%
Other techniques focus on constructing ``features'' that are rotation-invariant \cite{flusser2000independence, lowe1999object, sadler1992shift, ojala2002multiresolution}, and then using these features (rather than the images themselves) in further analyses and computations.
%
However, such features are often problem-dependent, and developing rotation-invariant features that are stable to noise and deformations is still an active area of research.
%
One can also construct algorithms that are invariant to rotations of the images \cite{hilai1004recognition, zhao2013fourier}.
%
However,

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\textwidth]{vdm_2d_time_corr}
\caption{}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\foreach \n in {1,9,17,25,30,34,38,43,49}{
\includegraphics[width=0.3\textwidth]{dpERK_vdm_\n}
\hfill}
\caption{}
\end{subfigure}
\caption{{\bf Ordering two-dimensional fluorescent images of dpERK.}
(a) Correlation between the VDM embedding coordinate and the membrane thickness. 
(b) Some representative fluorescent images, aligned  and ordered using the VDM embedding coordinate. }
\label{fig:vdm_image_ordering}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\textwidth]{DMAPS_scat_time_corr}
\caption{}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\foreach \n in {1,9,17,25,30,34,38,43,49}{
\includegraphics[width=0.3\textwidth]{dpERK_scat_\n}
\hfill}
\caption{}
\end{subfigure}
\caption{{\bf Ordering two-dimensional fluorescent images of dpERK.}
(a) Correlation between the first (non-trivial) DMAPS embedding coordinate and the membrane thickness. The DMAPS embedding was computed using the translation- and rotation-invariant scattering transform coefficients as ``features'' of the images.
(b) Some representative fluorescent images, ordered using the first (non-trivial) DMAPS embedding coordinate computed from the scattering transform coefficients. }
\label{fig:scattrans_dpERK_ordering}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\textwidth]{DMAPS_membrane_scat_time_corr}
\caption{}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\foreach \n in {1,9,17,25,30,34,38,43,49}{
\includegraphics[width=0.3\textwidth]{membrane_scat_\n}
\hfill}
\caption{}
\end{subfigure}
\caption{{\bf Ordering two-dimensional fluorescent images of membrane proteins.}
(a) Correlation between the seventh (non-trivial) DMAPS embedding coordinate and the membrane thickness. DMAPS was computed using the translation- and rotation-invariant scattering transform coefficients as ``features'' of the images. The first six non-trivial DMAPS coordinates were found to capture other features of the images, such as  differences in fluorescence intensity within the images.
(b) Some representative fluorescent images, ordered using the seventh (non-trivial) DMAPS embedding coordinate computed from the scattering transform coefficients. }
\label{fig:scattrans_membrane_ordering}
\end{figure}

@@

\subsection*{Image Preprocessing}
The dpERK images we collect from the confocal microscope are subsampled to $100 \times 100$ pixels; the membrane images are subsampled to $200 \times 200$ pixels (due to the finer features in the membrane pictures).

@@

The scattering transform consists of a wavelet transform of the signal, followed by  the appropriate averaging operator.
%
This transform is applied to the signal itself, as well as to the residual, in order to preserve as much information about the signal itself, while still keeping the transform coefficients translation- and rotation-invariant. 
% 
Furthermore, the scattering transform can be shown to be a contractive operator; therefore, noise and small deformations in the signal are not amplified in the transformation.

\subsection*{Edge detection}
For the membrane images, we are only interested in the location of the edges of the membrane (not other features, such as the intensity of the fluorescent stain).
%
We therefore preprocess the

@@

Spearman's rank correlation coefficient, or Spearman's $\rho$, measures the monotonicity of a function \cite{...}. 
%
It therefore serves as an appropriate metric for the ``goodness'' of our orderings.
%
Given data points $X_i$ and $Y_i$, we compute the ranks of each data point within the data set, denoted $x_i$ and $y_i$.
%
Spearman's $\rho$ is then defined as the correlation between the ranks
\begin{equation}
\rho = \frac{\sum_i (x_i - \overline{x})(y_i - \overline{y})}{\sqrt{\sum_i (x_i - \overline{x})^2 \sum_i (y_i - \overline{y})^2}}
\end{equation}

>>>>

The issue of rotation invariance arises in many applications, such as medical imaging \cite{hajnal2010medical}, face recognition \cite{rowley1998rotation}, digit recognition \cite{simard1992efficient}, and texture classification \cite{greenspan1994rotation}.
%
In these settings, objects from different frames or timepoints must be aligned or ``registered'' before further analysis can be done.
%
%For example, often medical images (such as MRI scans) are collected over multiple days, and doctors would like to study development of a condition (such as the growth of a tumor).
%
%However, on each day, the patient and/or sensors may be in slightly different locations; therefore, the images must be aligned before the doctor can look at how the tumor is growing and evolving.
%
Several different techniques have been developed to solve the image registration problem. 
%
``Template-based'' techniques are relatively common, where one selects a prototypical image or ``template'', and then aligns the remaining images to this template \cite{ahuja2007template}.
%
Such techniques can suffer if a good template is not know {\em a priori}; when the images are noisy, selecting one image from the data set at random can yield a noisy template and result in many mis-alignments. 
%
Other techniques focus on constructing ``features'' that are rotation-invariant \cite{flusser2000independence, lowe1999object, sadler1992shift, ojala2002multiresolution}, so that one can use these features (rather than the images themselves) in further analyses and computations.
%
However, constructing rotation-invariant features that still retain the important information in the images is difficult and often problem-dependent, and developing rotation-invariant features that are stable to noise and deformations is still an active area of research \cite{mallat2012group, sifre2013rotation}.
%
One can also construct algorithms that are invariant to rotations of the images \cite{hilai1994recognition, zhao2013fourier}.
%
ADD WHY THIS IS BAD.

@@

\begin{figure}[H]
\centering
\begin{subfigure}{\textwidth}
\centering
\includegraphics[width=0.7\textwidth]{vdm_2d_time_corr}
\caption{}
\end{subfigure}
\begin{subfigure}{\textwidth}
\foreach \n in {1,9,17,25,30,34,38,43,49}{
\includegraphics[width=0.07\textwidth, trim=6in 0in 6in 0in, clip]{dpERK_vdm_\n}
\hfill}
\caption{}
\end{subfigure}
\caption{{\bf Ordering two-dimensional fluorescent images of dpERK.}
(a) Correlation between the VDM embedding coordinate and the membrane thickness. 
(b) Some representative fluorescent images, aligned  and ordered using the VDM embedding coordinate. }
\label{fig:vdm_image_ordering}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{subfigure}{\textwidth}
\includegraphics[width=0.7\textwidth]{DMAPS_scat_time_corr}
\caption{}
\end{subfigure}
\begin{subfigure}{\textwidth}
\foreach \n in {1,9,17,25,30,34,38,43,49}{
\includegraphics[width=0.07\textwidth, trim=6in 0in 6in 0in, clip]{dpERK_scat_\n}
\hfill}
\caption{}
\end{subfigure}
\caption{{\bf Ordering two-dimensional fluorescent images of dpERK.}
(a) Correlation between the first (non-trivial) DMAPS embedding coordinate and the membrane thickness. The DMAPS embedding was computed using the translation- and rotation-invariant scattering transform coefficients as ``features'' of the images.
(b) Some representative fluorescent images, ordered using the first (non-trivial) DMAPS embedding coordinate computed from the scattering transform coefficients. }
\label{fig:scattrans_dpERK_ordering}
\end{figure}

@@

$\rho = 0.8403$

$\rho = 0.3525$ for VDM + membrane pics

\begin{figure}[H]
\centering
\begin{subfigure}{\textwidth}
\centering
\includegraphics[width=0.7\textwidth]{DMAPS_membrane_scat_time_corr}
\caption{}
\end{subfigure}
\begin{subfigure}{\textwidth}
\foreach \n in {1,9,17,25,30,34,38,43,49}{
\includegraphics[width=0.07\textwidth, trim=6in 0in 6in 0in, clip]{membrane_scat_\n}
\hfill}
\newline
\foreach \n in {1,9,17,25,30,34,38,43,49}{
\includegraphics[width=0.07\textwidth, trim=6in 0in 6in 0in, clip]{membrane_scat_raw_\n}
\hfill}
\caption{}
\end{subfigure}
\caption{{\bf Ordering two-dimensional fluorescent images of membrane proteins.}
(a) Correlation between the seventh (non-trivial) DMAPS embedding coordinate and the membrane thickness. DMAPS was computed using the translation- and rotation-invariant scattering transform coefficients as ``features'' of the images. The first six non-trivial DMAPS coordinates were found to capture other features of the images, such as  differences in fluorescence intensity within the images.
(b) Some representative fluorescent images, ordered using the seventh (non-trivial) DMAPS embedding coordinate computed from the scattering transform coefficients. }
\label{fig:scattrans_membrane_ordering}
\end{figure}

@@

\subsection*{Image Preprocessing}
The dpERK images we collect from the confocal microscope are subsampled to $100 \times 100$ pixels; the membrane images are subsampled to $200 \times 200$ pixels (due to the finer structure in the membrane pictures).

@@

The scattering transform consists of a wavelet transform of the signal, followed by  the appropriate averaging operator.
%
This transform is applied to the signal itself, as well as to the residual, in order to preserve as much information about the signal itself, while still keeping the transform coefficients translation- and rotation-invariant. 
% 
Furthermore, the scattering transform can be shown to be a contractive operator; therefore, noise and small deformations in the signal are not amplified in the transformation.
%
We utilized the freely available ScatNet software (\texttt{http://www.di.ens.fr/data/software/scatnet/}) to compute the rotation-invariant scattering coefficients.

@@

Spearman's rank correlation coefficient, or Spearman's $\rho$, measures the monotonicity of a function \cite{...}. 
%
It therefore serves as an appropriate metric for the ``goodness'' of our orderings.
%
Given data points $X_i$ and $Y_i$, we compute the ranks of each data point within the data set, denoted $x_i$ and $y_i$.
%
Spearman's $\rho$ is then defined as the correlation between the ranks
\begin{equation}
\rho = \frac{\sum_i (x_i - \overline{x})(y_i - \overline{y})}{\sqrt{\sum_i (x_i - \overline{x})^2 \sum_i (y_i - \overline{y})^2}}
\end{equation}
where $\overline{x}$ and $\overline{y}$ are the averages of $x_i$ and $y_i$, respectively.
